SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-09-20 scipy-1.0/paper.tex
Add note to include NumPy 1.0 release date

In 2000, STScI ported their entire IDL-based analysis pipeline, IRAF,
to Python.  And it was here that a small crisis developed around the
Python numerical array container.  Numeric, the original array package, was
suitable for small arrays, but not for the large images processed by
STScI.  With the Numeric maintainer's blessing, the decision was made
to write NumArray, a library that could handle data on a different
scale.  Unfortunately, NumArray proved inefficient for small arrays,
presenting the community with a rather unfortunate choice.  In 2005,
Travis Oliphant combined the best elements of Numeric and NumArray,
thereby solving the dilemma and paving the way for Python to become
a very significant player in the Data Science movement.

>>>>

In 2000, STScI ported their entire IDL-based analysis pipeline, IRAF,
to Python.  And it was here that a small crisis developed around the
Python numerical array container.  Numeric, the original array package, was
suitable for small arrays, but not for the large images processed by
STScI.  With the Numeric maintainer's blessing, the decision was made
to write NumArray, a library that could handle data on a different
scale.  Unfortunately, NumArray proved inefficient for small arrays,
presenting the community with a rather unfortunate choice.  In 2005,
Travis Oliphant combined the best elements of Numeric and NumArray,
thereby solving the dilemma and paving the way for Python to become
a very significant player in the Data Science movement.\fixme{NumPy
  1.0 was released in October 2006}
